---
title: "CKKS encode encrypt"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CKKS encode encrypt}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load libraries that will be used.
```{r setup}
library(polynom)
library(HomomorphicEncryption)
```

Set a working seed for random numbers (so that random numbers can be replicated exactly).
```{r seed}
set.seed(123)
```

Set some parameters.
```{r params}
M     <- 8
N     <- M / 2
scale <- 200
xi    <- complex(real = cos(2 * pi / M), imaginary = sin(2 * pi / M))
```

Create the (complex) numbers we will encode.

```{r z}
z <- c(complex(real=3, imaginary=4), complex(real=2, imaginary=-1))
print(z)
```

Now we encode the vector of complex numbers to a polynomial.

```{r encode}
m <- encode(xi, M, scale, z)
```

Let's view the result.

```{r print-p}
print(m)
```

Set some parameters.
```{r params2}
d  =   4
n  =   2^d
p  =   (n/2)-1
q  = 874
pm = GenPolyMod(n)
```

Create the secret key and the polynomials a and e, which will go into the public key
```{r seckey}
# generate a secret key
s = GenSecretKey(n)

# generate a
a = GenA(n, q)

# generate the error
e = GenError(n)
```

Generate the public key.
```{r pubkey}
pk0 = GenPubKey0(a, s, e, pm, q)
pk1 = GenPubKey1(a)
```

Create polynomials for the encryption
```{r}
# polynomials for encryption
e1 = GenError(n)
e2 = GenError(n)
u  = GenU(n)
```

Generate the ciphertext
```{r}
ct0 = CoefMod((pk0*u + e1 + m) %% pm, q)
ct1 = EncryptPoly1(pk1, u, e2, pm, q)
```

Decrypt
```{r}
decrypt = (ct1 * s) + ct0
decrypt = decrypt %% pm
decrypt = CoefMod(decrypt, q)
print(decrypt[1:length(m)])
```


Let's decode to obtain the original number:

```{r decode}
decoded_z <- decode(xi, M, scale, polynomial(decrypt[1:length(m)]))
print(decoded_z)
```

The decoded z is indeed very close to the original z, we round the result to make the clearer.

```{r round}
round(decoded_z)
```
