---
title: "BGV addition 2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BGV addition 2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(polynom)
library(HomomorphicEncryption)
```

Set some parameters.
```{r params}
d  =   4
n  =   2^d
p  =   (n/2)-1
q  = 868
```

Set a working seed for random numbers
```{r}
set.seed(123)
```

Here we create the polynomial modulo.

```{r GenPolyMod}
pm = polynomial( coef=c(1, rep(0, n-1), 1 ) )
print(pm)
```

Create the secret key.

```{r secretkey}
# generate a secret key
s = polynomial( sample.int(3, n, replace=TRUE)-2 )
print(s)
```

Create a (part of the public key)

```{r a}
# generate a
a = polynomial(sample.int(q, n, replace=TRUE))
print(a)
```

Create the error term `e` to be used to generate the public key.

```{r e}
# generate the error
e = polynomial( coef=round(stats::rnorm(n, 0, n/3)) )
print(e)
```

Generate Part 1 of the Public Key.

```{r pubkey1}
pk1 = -(a*s + p*e)
pk1 = pk1 %% pm
pk1 = CoefMod(pk1, q)
print(pk1)
```

Generate Part 2 of the Public Key (which is actually just equal to a).

```{r pubkey2}
pk2 = a
```

Create a polynomial message
```{r}
# create a message
m = polynomial( coef=c(3, 2, 1) )
```

Create polynomials for the encryption of the message. Since e1 and e2 are constructed the same way as e, we don't print them, we just print u.

```{r e1e2u}
# polynomials for encryption
e1 = polynomial( coef=round(stats::rnorm(n, 0, n/3)) )
e2 = polynomial( coef=round(stats::rnorm(n, 0, n/3)) )
u  = polynomial( coef=sample.int(3, (n-1), replace=TRUE)-2 )
print(u)
```

Generate Part 1 of the ciphertext version of the message.

```{r ciphertext1}
ct1 = pk1*u + p*e1 + m
ct1 = ct1 %% pm
ct1 = CoefMod(ct1, q)
print(ct1)
```

Generate Part 2 of the ciphertext version of the message.

```{r ciphertext2}
ct2 = pk2*u + p*e2
ct2 = ct2 %% pm
ct2 = CoefMod(ct2, q)
print(ct2)
```

Now we take our message (3,2,1) and add it to itself - while encrypted:

```{r evaladd}
ct1sum = ct1 + ct1
ct2sum = ct2 + ct2
```

Decrypt

```{r}
decrypt = (ct2sum * s) + ct1sum
decrypt = decrypt %% pm
decrypt = CoefMod(decrypt, q)
decrypt = CoefMod(round(decrypt), p)
print(decrypt)
```
